---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  dpi = 600,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mapindia

<!-- badges: start -->
[![R-CMD-check](https://github.com/shubhamdutta26/mapindia/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/shubhamdutta26/mapindia/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/shubhamdutta26/mapindia/graph/badge.svg)](https://app.codecov.io/gh/shubhamdutta26/mapindia)
<!-- badges: end -->

The goal of mapindia is to simplify mapping of the Indian subcontinent. It has convenient functions for plotting choropleths, visualizing spatial data, and handling state/district codes.

**Note:** The 3-digit district codes were merged with the 2-digit state codes to create a 5-digit district code.

## Installation

To install mapindia from CRAN:

```{r}
#| label: cran
#| eval: false
install.packages("mapindia")
```


You can install the development version of mapindia from [GitHub](https://github.com/) with:

```{r}
#| label: github
#| eval: false
# install.packages("pak")
pak::pak("shubhamdutta26/mapindia")
```
## Usage

``` {r}
#| label: load
#| eval: false
library(mapindia)
```

## Example

Plot a basic map of the Indian subcontinent with states and districts:

```{r states-dist}
library(mapindia)
library(ggplot2)
library(cowplot)

states <- plot_india("states") +
  geom_sf(fill= "antiquewhite") +
  theme(panel.grid.major = 
          element_line(color = gray(.5), linetype = "dashed", linewidth = 0.2), 
        panel.background = element_rect(fill = "aliceblue"))

districts <- plot_india("districts") +
  geom_sf(fill= "gray") +
  theme(panel.grid.major = 
          element_line(color = gray(.5), linetype = "dashed", linewidth = 0.2), 
        panel.background = element_rect(fill = "aliceblue"))

cowplot::plot_grid(states, districts, nrow = 1)
```

Visualize zones such as the Central or Eastern Zonal Councils:

```{r zones, warning=FALSE}
central <- plot_india("states", include = .central, exclude = "UK", labels = TRUE) +
  geom_sf(fill= "antiquewhite")

east <- plot_india("states", include = .east, labels = FALSE)

cowplot::plot_grid(central, east, nrow = 1)
```

Visualize individual states such as the West Bengal or Tamil Nadu:

```{r states, warning=FALSE}
mh <- plot_india("districts", include = "MH")

tn <- plot_india("state", include = "Tamil Nadu", labels = FALSE)

cowplot::plot_grid(mh, tn, nrow = 1)
```

Use your data for visualizations as well:

```{r data, warning=FALSE}
statepop2011 <- plot_india("states", data = statepop, values = "pop_2011") +
  scale_fill_continuous(low = "blue", high = "yellow", guide = "none")

wbpop2011 <- plot_india("districts", data = wb_2011, values = "pop_2011", include = "WB") +
  scale_fill_continuous(low = "green", high = "red", guide = "none")

cowplot::plot_grid(statepop2011, wbpop2011, nrow = 1)
```
